\input{utilities}

% ---------- PERSONAL INFO ----------
\def\firstname{Shivanshu}
\def\lastname{Srivastava}
\def\location{Varanasi, India -- 221010}
\def\phone{+91 9198865041}
\def\email{shivanshu.srivastava.work@gmail.com}
\def\linkedin{https://www.linkedin.com/in/srivastavashivanshu/}
\def\github{https://github.com/brrrezy}

% Shorthand for bullet list blocks used inside entries
\def\bullets{\resumeItemListStart}
\def\bullet{\resumeItem}
\def\bulletsEnd{\resumeItemListEnd}

% ---------- SUMMARY ----------
\def\summary{
  \section{Professional Summary}
  Motivated and results-oriented B.Tech Computer Science student specializing in Python development, automated scripting, and backend engineering. Hands-on experience designing RESTful APIs with FastAPI and Flask, implementing RAG pipelines with LangChain and vector databases, and engineering robust web scrapers. Skilled in relational and non-relational database integration, Git-based workflows, and writing clean, object-oriented code. Quick learner with a problem-solving mindset seeking a Python Developer / Backend Engineer role.
}

% ---------- SKILLS ----------
\def\skills{
  \bullets
    \bullet{Languages: Python 3.x, SQL, HTML/CSS, Bash}
    \bullet{Frameworks \& Libs: FastAPI, Flask, Django, Pandas, NumPy, BeautifulSoup, Requests, LangChain}
    \bullet{Databases: PostgreSQL, SQLite, MongoDB, MySQL, SQLAlchemy ORM}
    \bullet{Tools \& Platforms: Git, GitHub, VS Code, Postman, Linux/Ubuntu, Docker, Jupyter Notebook}
    \bullet{Core Concepts: REST APIs, OOP (Object-Oriented Programming), Data Structures \& Algorithms, Web Scraping, Automation}
    \bullet{Testing: Pytest, Unit Testing, Debugging, Code Review}
  \bulletsEnd
}

% ---------- EDUCATION ----------
\EducationEntry{College}
  {2022}{Present}
  {Sandip University}
  {B.Tech}{Computer Science and Engineering}
  {Nashik, Maharashtra}

\EducationEntry{School}
  {2018}{2021}
  {GlenHill School}
  {SSC \& HSC}{}
  {Varanasi, Uttar Pradesh}

% ---------- INTERNSHIPS ----------
\InternshipEntry{BrainOVision}
  {Jan 2024}{Mar 2024}
  {Machine Learning Intern}
  {Brain O Vision}
  {Hyderabad, India}
  {
    \bullets
      \bullet{Fine-tuned XGBoost and Random Forest models on consumer datasets to assist in improving predictive accuracy.}
      \bullet{Developed feature engineering pipelines and behavioral clustering models to preprocess customer data.}
      \bullet{Collaborated on a customer segmentation project using K-Means to identify distinct user cohorts for marketing analysis.}
    \bulletsEnd
  }

\InternshipEntry{CodeAlpha}
  {Nov 2025}{Nov 2025}
  {Python Programming Intern}
  {Code Alpha}
  {Lucknow, India}
  {
    \bullets
      \bullet{Wrote asynchronous Python scripts to automate routine tasks and optimize data processing workflows.}
      \bullet{Implemented unit tests to increase codebase reliability and identify bugs during active development cycles.}
      \bullet{Refactored older scripts into modular, object-oriented structures to improve code readability and maintenance.}
    \bulletsEnd
  }

% ---------- PROJECTS ----------

\ProjectEntry{TradeFlow}
  {}
  {TradeFlow -- Trading Workspace}
  {\href{https://thetradeflow.vercel.app}{Live} $|$ Python, FastAPI, MongoDB, LangChain, Next.js}
  {
    \bullets
      \bullet{Built a high-performance REST API with FastAPI supporting real-time data streaming and trade ingestion.}
      \bullet{Designed a flexible MongoDB schema with isolated per-user data architectures; integrated secure JWT authentication.}
      \bullet{Engineered an AI coaching module with LangChain and LLMs to parse execution logs and discover trading behavioral biases.}
    \bulletsEnd
  }

\ProjectEntry{NSEScreener}
  {}
  {NSE Swing Screener}
  {\href{https://findswingstocks.up.railway.app/}{Live} $|$ Python, FastAPI, SQLite, BeautifulSoup, APScheduler}
  {
    \bullets
      \bullet{Developed a quantitative stock screener scanning 500+ NSE stocks in parallel, lowering scanning runtime to under 60 seconds.}
      \bullet{Implemented Minervini Stage 2 and Volatility Contraction Pattern (VCP) detection mathematical algorithms on historical data.}
      \bullet{Utilized BeautifulSoup to scrape stock metrics and integrated SQLite as a local caching layer to optimize API rate-limits.}
    \bulletsEnd
  }

\ProjectEntry{DietGPT}
  {}
  {DietGPT}
  {\href{https://fixyourdiet.vercel.app}{Live} $|$ Flask, Firebase, LangChain, Groq}
  {
    \bullets
      \bullet{Built a fitness assistant leveraging LangChain and Groq LLMs to generate personalized meal plans based on user profiles.}
      \bullet{Integrated a pipeline for parsing food entries and delivering instant calorie and macronutrient estimations.}
    \bulletsEnd
  }

\ProjectEntry{NSEBreakoutMonitor}
  {}
  {NSE Momentum Burst Scanner}
  {\href{https://github.com/brrrezy/NSE-Breakout-Monitor}{Source} $|$ Python, BeautifulSoup, GitHub Actions, Telegram API}
  {
    \bullets
      \bullet{Engineered an automated script running daily on GitHub Actions to scan Nifty 500 stocks for high-probability breakouts.}
      \bullet{Parsed HTML pages using BeautifulSoup to track stock trend confluences (RSI, ADX, MACD, and stochastic momentum).}
      \bullet{Integrated the Telegram Bot API to dispatch instant alert watchlists directly to active channel subscribers.}
    \bulletsEnd
  }

\ProjectEntry{AeronexisAI}
  {}
  {Aeronexis AI}
  {\href{https://aeronexis.vercel.app}{Live} $|$ Next.js, Tailwind CSS, Framer Motion, MongoDB}
  {
    \bullets
      \bullet{Designed a responsive landing page and waitlist registration system for an engineering simulation platform.}
      \bullet{Integrated MongoDB Atlas to store pre-registration contact details and user sign-ups securely.}
    \bulletsEnd
  }

\ProjectEntry{ShootersOfIndia}
  {}
  {Shooters of India}
  {\href{https://shootersofindia.com}{Live} $|$ HTML/CSS, JavaScript}
  {
    \bullets
      \bullet{Designed and deployed a search-optimized e-commerce website for sports shooting accessories, improving search visibility.}
      \bullet{Integrated Google Analytics to track user traffic, session engagement, and conversion metrics.}
    \bulletsEnd
  }

\ProjectEntry{ClimaCast}
  {}
  {Clima-Cast}
  {\href{https://github.com/brrrezy/Clima-Cast}{Source} $|$ Python, scikit-learn}
  {
    \bullets
      \bullet{Trained an MLPRegressor model to predict ambient temperature and humidity using historical weather datasets.}
      \bullet{Built a basic data pipeline for cleaning raw data, formatting inputs, and visualizing prediction accuracy.}
    \bulletsEnd
  }

\ProjectEntry{ThirdEye}
  {}
  {Autonomous Organizational Memory (ThirdEye)}
  {\href{https://github.com/brrrezy/Third-Eye}{Source} $|$ Python, ChromaDB, RAG, LangChain, FastAPI}
  {
    \bullets
      \bullet{Created a Retrieval-Augmented Generation (RAG) platform to query system logs and corporate documentation.}
      \bullet{Integrated ChromaDB vector database for semantic search, custom text chunking, and similarity-based retrieval.}
      \bullet{Built FastAPI endpoints delivering natural language answers backed by custom source citations.}
    \bulletsEnd
  }

% ---------- HACKATHONS ----------
\ProjectEntry{SunHacks2026}
  {April 2026}
  {Regulatory Guideline Monitor \& Updater (Top 10)}
  {Sunhacks 2026}
  {
    \bullets
      \bullet{Developed a real-time, webhook-based compliance monitor tracking regulatory updates from NSE, BSE, MCX, and RBI.}
      \bullet{Engineered an interactive dashboard for visualizing policy updates and automating alerts for guideline changes.}
    \bulletsEnd
  }

\ProjectEntry{SunHacks}
  {April 2024}
  {HVAC Smart Control System (Top 10)}
  {Sunhacks 2024 by Sandip University \& ESDS}
  {
    \bullets
      \bullet{Designed a predictive model for HVAC energy optimization and climate control.}
    \bulletsEnd
  }

\ProjectEntry{HackAICTE}
  {Oct 2023}
  {Sales Prediction \& Product Performance Predictor Model}
  {AICTE Data Science Hackathon (Winner)}
  {
    \bullets
      \bullet{Built regression models and performed feature engineering on 1000+ records.}
    \bulletsEnd
  }